{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA

### 2021-08-18 paper/tex/sections/appendix.tex
add more appendix figures and rearrange to match

\subsection{Detection rate table}

@@

\subsection{Distribution of eccentric sources on sensitivity curve}
\begin{figure*}[hb]
    \centering
    \includegraphics[width=\textwidth]{fig13_dcos_on_sc_eccentric_colours.png}
    \caption{As the bottom panels of Fig.~\ref{fig:dcos_on_sc}, but without the density distributions and scatter points are coloured by their eccentricity. We show eccentric sources are located in an offshoot below the $30 \unit{kpc}$ around $2 \unit{mHz}$. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig13_dcos_on_sc_eccentric_colours.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/sensitivity_curve.ipynb}{\faBook}.}
    \label{fig:dcos_on_sc_ecc_col}
\end{figure*}

\subsection{Detection rates relative to fiducial model}
\begin{figure*}[hb]
    \centering
    \includegraphics[width=\textwidth]{fig14_dco_relative_rates.pdf}
    \caption{Similar to Fig.~\ref{fig:detection_rates}, this shows the \textit{relative} detection rates compared to the fiducial model in order to emphasise how much each DCO is affected by model variations compared to other DCOs. The scatter points show the mean and the shaded areas show the 1-$\sigma$ uncertainty range. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig14_dco_relative_rates.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
    \label{fig:dco_relative_rates}
\end{figure*}

\clearpage

\subsection{Formation channels}

\begin{figure}[h]
    \centering
    \includegraphics[height=0.85\textheight]{fig15_formation_channels.pdf}
    \caption{Fraction of each DCO type that is formed through different formation channels for all physics variations. Channels are described in detail in \citet{Broekgaarden+2021}. The classic, single core CEE and double core CEE channels all require at least one common-envelope event whilst only `only stable' consists of only stable mass transfer and `other' contains the remaining binaries which are mainly formed from `lucky' supernova kicks that shrink the binary. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig15_formation_channels.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/formation_channels.ipynb}{\faBook}. \todo{Update R and T}}
    \label{fig:formation_channels}
\end{figure}

>>>>

% \subsection{Detection rate table}

@@

% \subsection{Distribution of eccentric sources on sensitivity curve}
\begin{figure*}[b]
    \centering
    \includegraphics[width=\textwidth]{fig13_dcos_on_sc_eccentric_colours.png}
    \caption{As the bottom panels of Fig.~\ref{fig:dcos_on_sc}, but without the density distributions and scatter points are coloured by their eccentricity. We show eccentric sources are located in an offshoot below the $30 \unit{kpc}$ around $2 \unit{mHz}$. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig13_dcos_on_sc_eccentric_colours.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/sensitivity_curve.ipynb}{\faBook}.}
    \label{fig:dcos_on_sc_ecc_col}
\end{figure*}

% \subsection{Formation channels}

\begin{figure}[p]
    \centering
    \includegraphics[height=0.85\textheight]{fig15_formation_channels.pdf}
    \caption{Fraction of each DCO type that is formed through different formation channels for all physics variations. Channels are described in detail in \citet{Broekgaarden+2021}. The classic, single core CEE and double core CEE channels all require at least one common-envelope event whilst only `only stable' consists of only stable mass transfer and `other' contains the remaining binaries which are mainly formed from `lucky' supernova kicks that shrink the binary. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig15_formation_channels.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/formation_channels.ipynb}{\faBook}. \todo{Update R and T}}
    \label{fig:formation_channels}
\end{figure}

% \subsection{Properties of detectable systems (progenitors and at DCO formation)}
\begin{figure*}[ht]
    \centering
    \includegraphics[width=\textwidth]{progenitor_distributions.pdf}
    \includegraphics[width=0.66\textwidth]{dco_formation_distributions.pdf}
    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions}, but for the properties of the progentiors of detectable systems (top row) and the properties of the detectable systems at DCO formation (bottom row). Note that the $m_{1, {\rm ZAMS}}$ panel uses a log scaled $y$-axis. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/progenitor_distributions.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/dco_formation_distributions.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
    \label{fig:progenitor_and_dco_properties}
\end{figure*}

% \subsection{Detection rates relative to fiducial model}
\begin{figure*}[hb]
    \centering
    \includegraphics[width=\textwidth]{fig14_dco_relative_rates.pdf}
    \caption{Similar to Fig.~\ref{fig:detection_rates}, this shows the \textit{relative} detection rates compared to the fiducial model in order to emphasise how much each DCO is affected by model variations compared to other DCOs. The scatter points show the mean and the shaded areas show the 1-$\sigma$ uncertainty range. \todo{add R and T}. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig14_dco_relative_rates.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
    \label{fig:dco_relative_rates}
\end{figure*}

### 2021-08-18 paper/tex/sections/results.tex
add more appendix figures and rearrange to match

When comparing the distribution of formation times for the three different DCO types we see that NSNSs are most strongly concentrated at recent times, followed by BHBH and then BHNS. To understand this it is helpful to consider how the inspiral time scales with various parameters
\begin{equation}
    t_{\rm inspiral} = \frac{a^4}{(m_1 + m_2)^{3}} \cdot \frac{q}{(1+q)^2} \cdot (1 - e^2)^{-7/2}.
\end{equation}
The inspiral time depends most strongly on the separation at DCO formation ($a$) and this is where the three types also differ most strongly, see Fig.~\ref{fig:fiducial_pdf_distributions}{\bf X}. The NSNS systems have the tightest orbits at DCO formation. The median of the distribution of separations at DCO formation, $\langle a_{\rm DCO} \rangle_{\rm med}$, relate as 8:3:1 for BHBH:BHNS:NSNS in our simulations. This results in increase of the inspiral time by a factor of about 4000:80:1. The total masses affect the inspiral time to the third power and this where the heavier BHBH systems are favoured. The median total masses differ by ratios of 6:4:1 for BHBH:BHNS:NSNS in our simulations, impacting the inspiral times such that they are a factor of 200:60:1 shorter, partially counteracting the effect of the separations. The term depending on the mass ratio $q$ only varies by about 30\% for the mass ratio ranges considered here and is not of interest. The eccentricity term is not of importance for mildly eccentric systems, $f(e_{\rm DCO} \le 0.3)  \le 1.4$ but of large importance for the very eccentric  $f(e_{\rm DCO} \ge 0.9) \ge 300$. The fraction of highly eccentric systems with $e_{\rm DCO}>0.9$ is 33\%, 16\$ and 8\% of for BHBH, BHNS and NSNS respectively, see also Fig.~\ref{fig:fiducial_pdf_distributions}{\bf X}. 
%
We conclude that the shorter median separations at DCO formation are the main reason why NSNS are most strongly peaked at short delay times, followed by BHBH where the inspiral timescales are short because of their high masses and substantial eccentricities.

@@

\subsection{Progenitors and formation channels}\label{sec:progenitors_and_formation}
\todo{for tom: Refer to appendix figure on formation channel and birth initial mass, mass ratio metallicity (and separation).}

>>>>

When comparing the distribution of formation times for the three different DCO types we see that NSNSs are most strongly concentrated at recent times, followed by BHBH and then BHNS. To understand this it is helpful to consider how the inspiral time scales with various parameters
\begin{equation}
    t_{\rm inspiral} = \frac{a^4}{(m_1 + m_2)^{3}} \cdot \frac{q}{(1+q)^2} \cdot (1 - e^2)^{-7/2}.
\end{equation}
The inspiral time depends most strongly on the separation at DCO formation ($a$) and this is where the three types also differ most strongly, see Fig.~\ref{fig:progenitor_and_dco_properties}. The NSNS systems have the tightest orbits at DCO formation. The median of the distribution of separations at DCO formation, $\langle a_{\rm DCO} \rangle_{\rm med}$, relate as 8:3:1 for BHBH:BHNS:NSNS in our simulations. This results in increase of the inspiral time by a factor of about 4000:80:1. The total masses affect the inspiral time to the third power and this where the heavier BHBH systems are favoured. The median total masses differ by ratios of 6:4:1 for BHBH:BHNS:NSNS in our simulations, impacting the inspiral times such that they are a factor of 200:60:1 shorter, partially counteracting the effect of the separations. The term depending on the mass ratio $q$ only varies by about 30\% for the mass ratio ranges considered here and is not of interest. The eccentricity term is not of importance for mildly eccentric systems, $f(e_{\rm DCO} \le 0.3)  \le 1.4$ but of large importance for the very eccentric  $f(e_{\rm DCO} \ge 0.9) \ge 300$. The fraction of highly eccentric systems with $e_{\rm DCO}>0.9$ is 33\%, 16\$ and 8\% of for BHBH, BHNS and NSNS respectively, see also Fig.~\ref{fig:progenitor_and_dco_properties}. 
%
We conclude that the shorter median separations at DCO formation are the main reason why NSNS are most strongly peaked at short delay times, followed by BHBH where the inspiral timescales are short because of their high masses and substantial eccentricities.

@@

\subsection{Progenitors and formation channels}\label{sec:progenitors_and_formation}

Formation channel figure is Fig.~\ref{fig:formation_channels}.

Progenitor distribution figure is Fig.~\ref{fig:progenitor_and_dco_properties}.

\todo{for tom: Refer to appendix figure on formation channel and birth initial mass, mass ratio metallicity (and separation).}
